Flat histogram method comparison on 2D Ising Model

### 2020-04-17 ising/ising.tex
fixed the data script so the right data is used.
made notes for self on editing the ising paper.

\begin{abstract}
  We examine the convergence of the Stochastic Approximation with a Dynamic
  update factor (SAD) algorithm applied to the 2D ising model. Comparison with
  SAMC and WL methods show that SAD performs robustly and without user input
  knowledge of an energy range. We confirm that SAD is more powerful in the
  common case in which the range of energies is not known in advance. 
\end{abstract}

@@

\section{Introduction}
Flat histogram Monte-Carlo simulation algorithms calculate the thermodynamic
properties of various systems over a range of temperatures.  The first histogram
method used a single canonical Monte Carlo simulation to predict properties for
nearby temperatures~\cite{ferrenberg1988new}. While the method effectively
samples a narrow energy range given limited by a narrow temperature range, it
proves computationally inefficient at sampling large energy ranges.

@@

@@

@@

\jpsays{consider adding in minGamma WL here or before 1/t-WL method}

@@

\section{Results}
We tested the algorithms on two 2D Ising model systems.  The first is a smaller
simulation with a lattic size of 32 and the second has a lattice size of 128.
For each system we use a reasonable root-mean-square displacement distance
$\delta_0 = 0.05\sigma$ for proposed moves. The simulations explore the energy
space of the systems with minimum reduced temperatures of $T_{\text{min}} = 1$
for simulations All simulations lead to the minimum important energy $E_{\min}$
and maximum entropy energy $E_{\max}$ being calculated (with the exception of
the WL methods where both of these parameters are needed a priori).

@@

\section{Acknowledgments}
We thank Klas Markstr\"{o}m for discussions regarding the exact computation of the partition function for the 2D Ising model.

>>>>

\begin{abstract}
  We examine the convergence of the Stochastic Approximation with a Dynamic
  update factor (SAD) algorithm applied to the 2D ising model. Comparison with
  SAMC and WL methods show that SAD performs robustly and without user input
  knowledge of an energy range. We confirm that SAD is more powerful in the
  common case in which the range of energies is not known in advance.
  \jpsays{production run WL is also tested and does well} 
\end{abstract}

@@

\section{Introduction}

\jpsays{comment out the graphs we are not going to use i.e. the average entropy error.  Change Cv to cv in plots i.e. divide by 32 X 32 etc...}

Flat histogram Monte-Carlo simulation algorithms calculate the thermodynamic
properties of various systems over a range of temperatures.  The first histogram
method used a single canonical Monte Carlo simulation to predict properties for
nearby temperatures~\cite{ferrenberg1988new}. While the method effectively
samples a narrow energy range given limited by a narrow temperature range, it
proves computationally inefficient at sampling large energy ranges.

@@

\jpsays{here might be a good place to mention production run WL}

@@

\jpsays{add in the heat capacity formula here and comment out the average deviation form the exact solution for the entropy}

@@

\jpsays{consider adding in minGamma WL here or before 1/t-WL method.
An alternative method of implementing the WL algorithm is to first implement a “production” run~\cite{}. The WL method updates the weights w(E) until some Gamma min is reached. At this point, the weights are fixed and the method proceeds.}

@@

\section{Results}

\jpsays{this all needs rewritten in terms of heat capacity and WL min gamma.}
We tested the algorithms on two 2D Ising model systems.  The first is a smaller
simulation with a lattic size of 32 and the second has a lattice size of 128.
For each system we use a reasonable root-mean-square displacement distance
$\delta_0 = 0.05\sigma$ for proposed moves. The simulations explore the energy
space of the systems with minimum reduced temperatures of $T_{\text{min}} = 1$
for simulations All simulations lead to the minimum important energy $E_{\min}$
and maximum entropy energy $E_{\max}$ being calculated (with the exception of
the WL methods where both of these parameters are needed a priori).

@@

\section{Acknowledgments}

\jpsays{edit here!}
We thank Klas Markstr\"{o}m for discussions regarding the exact computation of the partition function for the 2D Ising model.
